Visualising How Non-linear Dimension Reduction Warps Your Data

### 2024-03-06 paper.qmd
Correct the issue getting same combinations of bins along x and y axes in PBMC data

## If same total number of bins ocurred only select ones with minimum error
duplicate_df_list <- mse_df_pbmc[duplicated(mse_df_pbmc$num_bins), ] |>
  dplyr::arrange(num_bins) |>
  dplyr::group_split(num_bins)

@@

  dd <- duplicate_df_list[[i]] |>
    dplyr::filter(mse == min(duplicate_df_list[[i]]$mse))

@@

mse_df_pbmc <- dplyr::bind_rows(mse_df_pbmc[!duplicated(mse_df_pbmc$num_bins), ], duplicate_df)
```

>>>>

## If same total number of bins occurred only select ones with minimum error
### Obtain duplicate bins
dupli_bins <- mse_df_pbmc |> 
  dplyr::count(num_bins) |> 
  dplyr::filter(n > 1) |> 
  dplyr::pull(num_bins)

duplicate_df_list <- mse_df_pbmc |>
  dplyr::filter(num_bins %in% dupli_bins) |>
  dplyr::arrange(num_bins) |>
  dplyr::group_split(num_bins)

@@

  dd <- duplicate_df_list[[i]] |>
    dplyr::filter(mse == min(duplicate_df_list[[i]]$mse)) |>
    dplyr::filter(hex_size == min(duplicate_df_list[[i]]$hex_size))

@@

not_dupli_df <- mse_df_pbmc |>
  dplyr::filter(!(num_bins %in% dupli_bins))

mse_df_pbmc <- dplyr::bind_rows(not_dupli_df, duplicate_df)
```
